The Astropy Project

### 2017-12-06 main.tex

\subsubsection{Defining functions that require quantities}
        When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct physical type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        These requirements often lead to implementing repetitive code for
        validating \texttt{Quantity} inputs.
        \texttt{astropy.units} now provides a \python decorator,
        \texttt{quantity\_input()}, that does this verification automatically.

>>>>

\subsubsection{Defining functions that require quantities}
        When writing code or
        functions that expect \texttt{Quantity} objects, we often want to
        enforce that the input units have the correct physical type.
        For example, we may want to require only length-type \texttt{Quantity}
        objects.
        \texttt{astropy.units} provides a tool called \texttt{quantity\_input()}
        that can perform this varification automatically to avoid repetitive
        code.
